Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-19 paper/paper.qmd

The results of the network analysis supports the restricted-broad groupings identified in @fig-seriation, and provides additional insights into the evolution of connectivity between groups. In the Transitional phase, the network analysis reveals two distinct and disconnected groups. The restricted group consists of Geissenklösterle, Fumane, and Pod Hradem, and the broad group consisting of Hohle Fels, El Castillo, and Labeko Koba, with no connections between the groups. The Proto-Aurignacian phase also shows two clearly defined groups, the broad group consisting of Geissenklösterle, Spy, Vogelherd, and Grotte du Renne, and the restricted group consisting of Mladeč, Hohlenstein-Stadel, Gatzarria, and Abri Pataud. However, it also displays some connectivity between the two groups of sites, with La Ferrassie connected to both groups. Les Cottés stands out with no connections to either group. The Early Aurignacian shows more strongly inter-connected groups -- although the shape still suggests two main groups -- with Grotte de la Verpillière I in particular having multiple strong connections to both groups. Lastly, the Evolved Aurignacian again shows two main groups, although intra-group connectivity has decreased, with the broad group consisting of Hohle Fels, Trou Magrite, Vogelherd, and Bockstein-Törle, and the restricted group consisting of Gargas, La Viña, Sirgenstein Cave, Vindija Cave, and Les Rois. As for the Early Aurignacian, inter-connectivity between groups continues to be evident in the Evolved Aurignacian, with connections between Trou Magrite, Gargas, and Vindija Cave, and Bockstein-Törle and Gargas, however the strength of inter-connectivity is weaker than in the Early Aurignacian.

>>>>

The results of the network analysis supports the restricted-broad groupings identified in @fig-seriation, and provides additional insights into the evolution of connectivity between groups. In the Transitional phase, the network analysis reveals one distinct and one disconnected group. The restricted group consists of Geissenklösterle, Fumane, and Pod Hradem, and the broad group consists of Hohle Fels, El Castillo, and Labeko Koba, with no connections between the groups. The Proto-Aurignacian phase also shows two clearly defined groups, the broad group consisting of Geissenklösterle, Spy, Vogelherd, and Grotte du Renne, and the restricted group consisting of Mladeč, Hohlenstein-Stadel, Gatzarria, and Abri Pataud. However, it also displays some connectivity between the two groups of sites, with La Ferrassie connected to both groups. Les Cottés stands out with no connections to either group. The Early Aurignacian shows more strongly inter-connected groups -- although the shape still suggests two main groups -- with Grotte de la Verpillière I in particular having multiple strong connections to both groups. Lastly, the Evolved Aurignacian again shows two main groups, although intra-group connectivity has decreased, with the broad group consisting of Hohle Fels, Trou Magrite, Vogelherd, and Bockstein-Törle, and the restricted group consisting of Gargas, La Viña, Sirgenstein Cave, Vindija Cave, and Les Rois. As for the Early Aurignacian, inter-connectivity between groups continues to be evident in the Evolved Aurignacian, with connections between Trou Magrite, Gargas, and Vindija Cave, and Bockstein-Törle and Gargas, however the strength of inter-connectivity is weaker than in the Early Aurignacian.
